### 2019-04-05 Thesis_Latex/ThesisFinal/Chapter4/Chapter4.tex
update final thesis

\chapter{Moving Obstacle Avoidance}
In this chapter we present an Obstacle Avoidance alghorithm based on Adaptive Model Predictive Control. First we introduced the case-study model, then we designed the controller and the method of decision-making. Finally we verified the proposed strategy in different scenarios.

@@

This is possible if and only if there is a free lane or  sufficient space for overtaking the obstacle. In the case the road is busy with vehicles, the ATLASCAR2 must slow down and adapts its speed to that of the closest obstacle until the scenario changes.

@@

where $C_L$ is the car length. When the velocity is zero then the rate of change of heading angle is zero, that is, it is not possible to change the vehicle's orientation
when it is not moving. If the front wheel is orthogonal to the back wheel, i.e. the steering angle is $\frac{\pi}{2}$, the ATLASCAR2 cannot move forward and the model enters an undefined region. In order to simplify the model, it is assumed that only the front wheel can be steered. Moreover, in this chapter it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance. Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle. In particular the rate of change of heading angle is referred to as turn rate which can be evaluated with a gyroscope. This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius. We can write the non-holonomic constraint which is an expression for velocity in the vehicle's $y$-direction in the world coordinate frame as follows:
\begin{equation}
	\dot{y}\cos\theta-\dot{x}\cos\theta=0.
\end{equation}

@@

Finally we can analyze time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle. Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral position of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from 0 can be noted regarding the $y$ coordinate due to the overcoming of the obstacle. 
To confirm a uniform trend, the speed of the ATLASCAR2 remains fairly constant. Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then come back to the cruising speed in the second part. Instead from the remaining Figures \ref{fig:throttle_one_moving}, \ref{fig:delta_one_moving} and \ref{fig:theta_one_moving} we can observe that the throttle $T$ and the steering angle $\delta$ respect the limits we imposed while the heading angle $\theta$ is used to describe the direction the ATLASCAR2 is pointing.
% RESULTS ONE MOVING OBSTACLE
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_one_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
	\label{fig:components_one_moving_obstacle}
\end{figure}

@@

This situation is represented in Figure \ref{fig:obstacleAvoidance_random}
where there are three different scenarios with $N = 2,3 \text{ and } 4$ moving obstacles that drive with a constant velocity of \SI{8}{m/s} in the opposite direction with respect to the ATLASCAR2. The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road. If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
% MULTIPLE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

In the Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion. We also improved the code infact in case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation. The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario. 
% SIX MOVING OBSTACLES
\begin{figure}[b!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_6.pdf}
	\end{minipage}
	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
	\label{fig:obstacleAvoidance_six_obstacles}
\end{figure}

>>>>

\chapter{Moving Obstacle Avoidance System}
In this chapter we present an Obstacle Avoidance alghorithm based on Adaptive Model Predictive Control. First we introduced the case-study model, then we designed the controller and the method of decision-making. Finally we verified the proposed strategy in different scenarios.

@@

This is possible if and only if there is a free lane or enough space to overcome the obstacle. If the road is occupied by vehicles, the ATLASCAR2 must slow down and adjust its speed to that of the nearest obstacle until the scenario changes.

@@

where $C_L$ is the car length. When the velocity is zero then the rate of change of heading angle is zero, that is, it is not possible to change the vehicle's orientation
when it is not moving. If the front wheel is orthogonal to the back wheel, i.e. the steering angle is $\frac{\pi}{2}$, the ATLASCAR2 cannot move forward and the model enters an undefined region. In order to simplify the model, it is assumed that only the front wheel can be steered. Moreover, in this chapter it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance. Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle. In particular the rate of change of heading angle is referred to as turn rate which can be evaluated with a gyroscope. This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius. We can write the non-holonomic constraint which is an expression for velocity in the ATLASCAR2's $y$-direction in the world coordinate frame as follows:
\begin{equation}
	\dot{y}\cos\theta-\dot{x}\cos\theta=0.
\end{equation}

@@

Finally we can analyze time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle. Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral positions of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from $0$ can be noted regarding the $y$ coordinate due to the overcoming of the obstacle. 
To confirm a uniform trend, the speed of the ATLASCAR2 remains fairly constant. Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then comes back to the cruising speed in the second part. Instead from the remaining Figures \ref{fig:throttle_one_moving}, \ref{fig:delta_one_moving} and \ref{fig:theta_one_moving} we can observe that the throttle $T$ and the steering angle $\delta$ respect the limits we imposed while the heading angle $\theta$ is used to describe the direction the ATLASCAR2 is pointing.
% RESULTS ONE MOVING OBSTACLE
\begin{figure}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
		\subcaption{}\label{fig:longitudinal_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
		\subcaption{}\label{fig:lateral_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
		\subcaption{}\label{fig:velocity_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
		\subcaption{}\label{fig:throttle_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
		\subcaption{}\label{fig:delta_one_moving}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
		\subcaption{}\label{fig:theta_one_moving}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
	\label{fig:components_one_moving_obstacle}
\end{figure}

@@

This situation is represented in Figure \ref{fig:obstacleAvoidance_random}
where there are three different scenarios with $N = 2,3 \text{ and } 4$ moving obstacles that drive with a constant velocity of \SI{8}{m/s} in the opposite direction with respect to the ATLASCAR2. The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road. If the $y$-coordinate of the closest obstacle is greater than $0$, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
% MULTIPLE MOVING OBSTACLE
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

In Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion. We also improved the code infact in case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation. The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario. 
% SIX MOVING OBSTACLES
\begin{figure}[b!]
	\centering
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\textwidth}
		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_6.pdf}
	\end{minipage}
	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
	\label{fig:obstacleAvoidance_six_obstacles}
\end{figure}
